---
title: "Untitled"
author: "Kriti Saxena"
date: '2022-10-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(forecast)
library(tidyverse)
library(lubridate)
library(plyr)
library(scales)
library(dplyr)
library(here)
```
# Clean and explore the data 

```{r}
library(here)
```

# change date to date format 
```{r pressure, echo=FALSE}
sales <- sales %>%
  mutate(Date = dmy(Date),
         Store = as.factor(Store))
```

```{r}
head(sales)
sales %>% summary()
str(sales)
head(sales)
dim(sales)
length(table(sales$Store))
colSums(is.na(sales))
all(duplicated(sales))
```

```{r}
sales %>%
  distinct(Store, Weekly_Sales) %>%
  group_by(Store) %>%
  summarize(mean_weekly_sales = mean(Weekly_Sales))
```
store 20 

```{r}
mean_sales <- aggregate(Weekly_Sales ~ Store, data = sales, mean)
mean_sales %>% 
  slice_max(order_by = Weekly_Sales, n=1)
```
Since store 20 has had most number of sales, we will predict if it will continue to keep up with the sales in upcoming year

```{r}
sales_1 <- sales %>% 
  filter(Store == 20)
```

```{r}
sales_1 %>%
  ggplot(aes(x=Date, y = Weekly_Sales)) + geom_line()
```
Since the graph is very cluttered, we will look at smaller time frames 

```{r}
sales_1 %>%
  filter(Date <= '2011-02-05') %>%
  ggplot(aes(x=Date, y = Weekly_Sales)) + geom_line()
```
```{r}
sales_1 %>%
  filter(Date > '2011-02-05' & Date < '2012-02-10') %>%
  ggplot(aes(x=Date, y = Weekly_Sales)) + geom_line()
```
```{r}
sales_1 %>%
  filter(Date > '2012-02-10' & Date < '2012-10-26') %>%
  ggplot(aes(x=Date, y = Weekly_Sales)) + geom_line()
```

After looking at the data in shorter time period, a similar period can be noticed every year. 
- The sales tends to increase in the month of December and between the months of April and May. 

```{r}
conv_month <- sales_1 %>%
  mutate(monthly = floor_date(Date,"month"))
```

```{r}
sum_monthly_sales <- aggregate(Weekly_Sales ~ monthly, data = conv_month, sum)
class(sum_monthly_sales)
```

```{r}
sum_monthly_sales<- sum_monthly_sales %>%
  mutate(sales = Weekly_Sales/1000000)
```

```{r}
sum_monthly_sales %>%
  ggplot(aes(x=monthly, y = sales)) + geom_line()
```
```{r}
# sales for months of 2010
sum_monthly_sales %>%
  filter(monthly < "2011-01-01") %>%
  ggplot(aes(x=monthly, y=sales)) + geom_line() 
```
```{r}
# sales for months of 2011
sum_monthly_sales %>%
  filter(monthly < "2012-01-01" & monthly > '2011-01-01') %>%
  ggplot(aes(x=monthly, y=sales)) + geom_line()
```

```{r}
# sales for month of 2012
sum_monthly_sales %>%
  filter(monthly > '2012-01-01') %>%
  ggplot(aes(x=monthly, y=sales)) + geom_line()
```
```{r}
sum_monthly_sales <- sum_monthly_sales %>%
  add_row(monthly = ymd(20100101), sales = 5.45) %>%
  arrange(monthly)
```

```{r}
sum_monthly_sales <- sum_monthly_sales %>%
  mutate(month = month(monthly))
```

```{r}
sum_monthly_sales$sales <- ts(sum_monthly_sales$sales)
sum_monthly_sales$month <- as.factor(sum_monthly_sales$month)
str(sum_monthly_sales)
```

```{r}
Model <- lm(sales ~ month, data = sum_monthly_sales)
summary(Model)
```

```{r}
ts_data <- ts(sum_monthly_sales$sales, frequency = 12)
data <- decompose(ts_data, "multiplicative")
plot(data)
```

```{r}
for_sarima <- ts(sum_monthly_sales$sales, start = 2010, frequency = 12)

# SARIMA
model <- auto.arima(for_sarima, D = 1)
summary(model)
```

```{r}
sales_p <- forecast(model, h = 14)
plot(sales_p)
p <- data.frame(summary(sales_p)$mean)
p
```

